Galaxy Zoo: Morphological Classifications for Galaxies in HST Legacy Imaging

### 2016-01-29 writeup/gz_hubble_data.tex
updated writeup with new debiasing info

\begin{figure}
\begin{center}
\includegraphics[width=0.50\textwidth]{figures/zeta_mu.pdf}
\caption{All fits for the vote fraction dropoff parameter $\zeta$ for $f_\textrm{features}$ in the \ferengi{} galaxies as a function of surface brightness. This includes only the 51~galaxies with a reasonably bounded range on the dropoff ($-10<\log(\zeta)<10$) and sufficient points to fit the function.}
\label{fig:zeta_mu}
\end{center}
\end{figure}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=\textwidth]{figures/p_vs_p_SB_redshift.pdf}
\caption{Effects of redshift bias in 3,959 images in the \ferengi{} sample. Each point in a given redshift and surface brightness bin represents a unique galaxy. On the y-axis in each bin is the $p_{features}$ value of the image of that galaxy redshifted to the value corresponding to that redshift bin. On the x-axis is the $p_{features}$ value of the image of the same galaxy redshifted to $z=0.3$. Regions in which there is a nearly one-to-one relationship between $p_{features}$ at high redshift and $z=0.3$ are white; those in which there is not are green, and those with not enough data ($N<5$) are purple. }
\label{fig:p_vs_p}
\end{center}
\end{figure*}

@@

Our criteria for determining whether a region of this space is single-valued, and therefore correctable, is as follows: For each surface brightness and redshift bin, we examine the distribution of $p_{\rm features,z=0.3}$ in four bins of $p_{\rm features,z}$. These sub-bins are marked by the horizontal lines within each larger, surface brightness/redshift bin in Figure~\ref{fig:p_vs_p}. First, we compute the interquartile range (IQR) of the distribution of $p_{\rm features,z=0.3}$ in each sub-bin, which are indicated by the orange bars. For the region to be considered correctable, we require that the IQR of the distribution within these sub-bins is less than the sub-bin height. Regions which fit these criteria are uncouloured in the plot. If the IQR is greater than the bin height, the region is considered uncorrectable; these are marked in green. Any region with fewer than 5 points is considered to have ``not enough information (NEI)'', and are shown in purple.

Using this approach, 52\% of the \ferengi{} images were found to have single-valued relationships between their $p_{\rm features}$ values at high and low redshift (see Table \ref{ferengi_corrections} for a summary.) Only these images were used in determining the $\zeta$ function (Section \ref{sec:zeta}).

\begin{table}
\caption{Distribution of \ferengi{} images analysed in Figure~\ref{fig:p_vs_p}. Correctable images had a single-valued relationship between their measured $p_{\rm features}$ values at high and low redshifts (white regions in Figure~\ref{fig:p_vs_p}). Uncorrectable images had a non single-valued relationship (green regions). NEI images had undetermined relationships due to a lack of data ($N<5$) in their corresponding sub-bins (purple regions).   \label{ferengi_corrections}}
\begin{tabular}{lcc}
\hline \hline
				   & N     & \% \\
\hline 
Correctable                        & 2,057   & 52\% \\
Uncorrectable                      & 1,732   & 44\% \\
NEI                                & 170     &  4\%\\
Total                              & 3,959   & 100\% \\
\hline \hline
\end{tabular}
\end{table}

>>>>

\begin{figure}
\begin{center}
\includegraphics[width=0.50\textwidth]{figures/zeta_mu.pdf}
\caption{All fits for the vote fraction dropoff parameter $\zeta$ for $f_\textrm{features}$ in the \ferengi{} galaxies as a function of surface brightness. This includes only the 37~galaxies with a reasonably bounded range on the dropoff ($-10<\log(\zeta)<10$) and sufficient points to fit the function.}
\label{fig:zeta_mu}
\end{center}
\end{figure}

@@

\begin{figure*}
\begin{center}
\includegraphics[width=\textwidth]{figures/p_vs_p_SB_redshift.pdf}
\caption{Effects of redshift bias in 3,950 images in the \ferengi{} sample. Each point in a given redshift and surface brightness bin represents a unique galaxy. On the y-axis in each bin is the $p_{features}$ value of the image of that galaxy redshifted to the value corresponding to that redshift bin. On the x-axis is the $p_{features}$ value of the image of the same galaxy redshifted to $z=0.3$. The dashed black lines represent the best-fit polynomials to the data in each square. The solid black line represents $p_{\rm features,z}$ = $p_{\rm features,z=0.3}$. Regions in which there is a single-valued relationship between $p_{features}$ at high redshift and $z=0.3$ are white; those in which there is not are blue, and those with not enough data ($N<5$) are gray. }
\label{fig:p_vs_p}
\end{center}
\end{figure*}

@@

Our criteria for determining whether a region of this space is single-valued, and therefore correctable, is as follows: In each surface brightness and redshift bin, we model the relationship between $p_{\rm features,z}$ and $p_{\rm features,z=0.3}$ by fitting the data with a polynomials of degrees 3, 2, and 1, and use the best fit out of the three. These fits are shown as the dashed black lines in figure ~\ref{fig:p_vs_p}. Any flat regions of the polynomial fits are areas in which there is not a clear single-valued relationship between $p_{\rm features,z}$ and $p_{\rm features,z=0.3}$; we quantify this by setting a minimum slope cut of 0.4. Any data in which the polynomial fit has a slope less than this value is considered \emph{not} one-to-one, and therefore ``uncorrectable.'' These regions are highlighted in blue in figure ~\ref{fig:p_vs_p}. Uncolored (white) regions of the plot have sufficiently high slopes for us to consider the relationship to be single-valued; galaxies in these regions are considered ``correctable'', and only these are used in measuring the parameters for the $\zeta$ function (Section \ref{sec:zeta}). Only surface brightness/redshift bins with at least 5 galaxies were considered; regions with fewer than 5 galaxies we consider to have 'not enough information' to determine the  $p_{\rm features,z}$ and $p_{\rm features,z=0.3}$ relationship, these are colored gray in figure ~\ref{fig:p_vs_p}.

\begin{table}
\caption{Distribution of \ferengi{} images analysed in Figure~\ref{fig:p_vs_p}. Correctable images had a single-valued relationship between their measured $p_{\rm features}$ values at high and low redshifts (white regions in Figure~\ref{fig:p_vs_p}). Uncorrectable images had a non single-valued relationship (green regions). NEI images had undetermined relationships due to a lack of data ($N<5$) in their corresponding sub-bins (purple regions).   \label{ferengi_corrections}}
\begin{tabular}{lrr}
\hline \hline
				   & N     & \% \\
\hline 
Correctable                        & 1,884   & 48\% \\
Uncorrectable                      & 1,986   & 50\% \\
NEI                                & 80     &  2\%\\
Total                              & 3,950   & 100\% \\
\hline \hline
\end{tabular}
\end{table}
